\documentclass[10pt, letterpaper]{article}

% ─── Packages ────────────────────────────────────────────────────────────────
\usepackage[
  top=0.55in, bottom=0.55in,
  left=0.65in, right=0.65in
]{geometry}
\usepackage{hyperref}
\usepackage{fontawesome5}
\usepackage{xcolor}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{multicol}
\usepackage{array}
\usepackage[T1]{fontenc}
\usepackage{lmodern}

% ─── Colors ──────────────────────────────────────────────────────────────────
\definecolor{accent}{HTML}{0EA5E9}
\definecolor{muted}{HTML}{64748B}
\definecolor{dark}{HTML}{1E293B}

% ─── Section Styling ─────────────────────────────────────────────────────────
\titleformat{\section}
  {\large\bfseries\color{dark}}
  {}{0em}{}
  [\vspace{-6pt}\rule{\linewidth}{0.6pt}\vspace{2pt}]
\titlespacing{\section}{0pt}{10pt}{4pt}

\setlength{\parindent}{0pt}
\pagestyle{empty}
\setlist[itemize]{leftmargin=*, nosep, topsep=2pt, itemsep=1pt}

% ─── Custom Commands ─────────────────────────────────────────────────────────
\newcommand{\entry}[4]{%
  \textbf{#1} \hfill \textit{\small\color{muted}#2} \\
  \textit{\color{muted}#3} \hfill \small\color{muted}#4 \\
  \vspace{2pt}
}

% ═════════════════════════════════════════════════════════════════════════════
\begin{document}
% ═════════════════════════════════════════════════════════════════════════════

% ─── Header ──────────────────────────────────────────────────────────────────
\begin{center}
  {\LARGE\bfseries\color{dark} SUDEEN JAIN H R} \\[4pt]
  {\large\color{accent} AI \& ML Engineer $|$ Full-Stack Developer} \\[6pt]
  \small
  \faIcon{map-marker-alt}~India \quad
  \faIcon{envelope}~\href{mailto:sudinhr1@gmail.com}{sudinhr1@gmail.com} \quad
  \faIcon{github}~\href{https://github.com/sudeenjain}{github.com/sudeenjain} \quad
  \faIcon{linkedin}~\href{https://linkedin.com/in/sudeenjain}{linkedin.com/in/sudeenjain}
\end{center}

\vspace{4pt}

% ─── Education ───────────────────────────────────────────────────────────────
\section{Education}
\entry{B.Tech in Artificial Intelligence \& Machine Learning}
      {2022 -- 2026}
      {Srinivas University, Mangalore, India}
      {Expected Graduation: May 2026}
\vspace{2pt}

% ─── Summary ──────────────────────────────────────────────────────────────────
\section{Summary}
Driven AI \& ML engineer with hands-on experience in building intelligent systems, cloud deployments, and full-stack web development. Proficient in Python, TensorFlow, AWS, Azure, and modern web frameworks. Passionate about turning data into actionable solutions.

\vspace{2pt}

% ─── Skills ──────────────────────────────────────────────────────────────────
\section{Technical Skills}
\begin{multicols}{2}
\begin{itemize}
  \item Python, Java, SQL, JavaScript, HTML/CSS
  \item TensorFlow, Scikit-learn, OpenCV, Pandas
  \item AWS (EC2, S3, Lambda), Azure, Google Cloud
  \item React, Node.js, Flask, FastAPI
  \item MySQL, PostgreSQL, Supabase, MongoDB
  \item Git, Docker, Linux, REST APIs
\end{itemize}
\end{multicols}

\vspace{2pt}

% ─── Projects (AUTO-GENERATED) ───────────────────────────────────────────────
\section{Projects}
\textbf{Game Level Difficulty Balancer} \hfill \textit{\small\color{muted}Jul 2026}\\ \small\href{https://github.com/sudeenjain/DAA-miniproject}{\color{accent}View Project}

\vspace{4pt}
\textbf{Book Recommender System} \hfill \textit{\small\color{muted}Jul 2026}\\ \small\href{https://github.com/sudeenjain/Adavanced-Java-BookRecommender}{\color{accent}View Project}

\vspace{4pt}
\textbf{IBM ML Recommender} \hfill \textit{\small\color{muted}Jul 2026}\\ \small\href{https://github.com/sudeenjain/IBM-miniproject}{\color{accent}View Project}

\vspace{4pt}
\textbf{Interactive Recipe Finder} \hfill \textit{\small\color{muted}Jul 2026}\\ \small\href{https://github.com/sudeenjain/-interactive-recipe-finder}{\color{accent}View Project}

\vspace{4pt}
\textbf{Currency Converter} \hfill \textit{\small\color{muted}Jul 2026}\\ \small\href{https://github.com/sudeenjain/currency-converter}{\color{accent}View Project}

\vspace{4pt}
\textbf{Smart To-Do List} \hfill \textit{\small\color{muted}Jul 2026}\\ \small\href{https://github.com/sudeenjain/to-do-list-in-python}{\color{accent}View Project}

\vspace{4pt}
\textbf{Gesture Flow} \hfill \textit{\small\color{muted}Jul 2026}\\ \small\href{https://github.com/sudeenjain/guesture\_flow}{\color{accent}View Project}

\vspace{4pt}
\textbf{Attendance Tracker} \hfill \textit{\small\color{muted}Jul 2026}\\ \small\href{https://github.com/sudeenjain/attendence\_tracker}{\color{accent}View Project}

\vspace{4pt}
\textbf{Movie Recommendation} \hfill \textit{\small\color{muted}Jul 2026}\\ \small\href{https://github.com/sudeenjain/Movie\_Recommendation}{\color{accent}View Project}

\vspace{4pt}
\textbf{Portfolio Website} \hfill \textit{\small\color{muted}Jul 2026}\\ \small\href{https://github.com/sudeenjain/portfolio}{\color{accent}View Project}

\vspace{4pt}
\textbf{FolioAI} \hfill \textit{\small\color{muted}Jul 2026}\\ \small\href{https://github.com/sudeenjain/folioAI}{\color{accent}View Project}

\vspace{4pt}
\textbf{CareerReady} \hfill \textit{\small\color{muted}Jul 2026}\\ \small\href{https://github.com/sudeenjain/CarrerReady}{\color{accent}View Project}

\vspace{4pt}
\textbf{Product Recommendation} \hfill \textit{\small\color{muted}Jul 2026}\\ \small\href{https://github.com/sudeenjain/Product\_Recommendation}{\color{accent}View Project}

\vspace{4pt}
\textbf{Connects The Dots} \hfill \textit{\small\color{muted}Jul 2026}\\ \small\href{https://github.com/sudeenjain/Connect\_the\_Dots}{\color{accent}View Project}

\vspace{4pt}
\textbf{Amazon Bestseller Recommender} \hfill \textit{\small\color{muted}Jul 2026}\\ \small\href{https://github.com/sudeenjain/Amazon-Bestseller-Recommender}{\color{accent}View Project}

\vspace{4pt}
\textbf{AI Dictionary} \hfill \textit{\small\color{muted}Jul 2026}\\ \small\href{https://github.com/sudeenjain/AI\_dictonary}{\color{accent}View Project}

% ─── Experience / Internships ────────────────────────────────────────────────
\section{Internships \& Experience}
\textbf{AI \& Machine Learning Internship}, \\
\begin{itemize}
  \item Built strong foundations in AI \textbackslash\{\}\& ML concepts, applied learning through practical tasks, and developed problem-solving skills aligned with industry expectations. Recognized under AICTE.
\end{itemize}

\vspace{4pt}
\textbf{Front-End Web Development Internship}, \\
\begin{itemize}
  \item Gained hands-on experience building responsive and interactive web pages, working with HTML, CSS, JavaScript, and modern frameworks. Strengthened UI/UX design principles and deployment skills. In collaboration with AICTE.
\end{itemize}

\vspace{4pt}
\textbf{Emerging Technologies — AI \& Cloud}, \\
\begin{itemize}
  \item Strengthened skills in AI and Cloud platforms while gaining hands-on exposure to real-world applications. In collaboration with AICTE and IBM.
\end{itemize}

\vspace{4pt}
\textbf{UI/UX Design Internship}, \\
\begin{itemize}
  \item Enhanced understanding of user-centered design and creative problem solving. Completed a 4-week online internship contributing meaningfully to design projects.
\end{itemize}

\vspace{4pt}
\textbf{Web Development Internship}, \\
\begin{itemize}
  \item Contributed to full-stack web development projects, building and debugging PHP backends and JavaScript frontends across multiple client products.
\end{itemize}

% ─── Certifications (AUTO-GENERATED) ────────────────────────────────────────
\section{Certifications}
\textbf{Project Management Fundamentals} --- IBM SkillsBuild \hfill \textit{\small\color{muted}Jul 17,}\\ \small ID: cRerp16F $\cdot$ \href{https://www.credly.com/go/cRerp16F}{\color{accent}Verify}\\ \small\color{muted} Earned the IBM SkillsBuild Project Management Fundamentals certificate, demonstrating foundational knowledge of project management principles, project planning, project lifecycle, risk management, stakeholder communication, and effective team collaboration.

\vspace{4pt}
\textbf{Lifelong Professional Skills} --- IBM SkillsBuild \hfill \textit{\small\color{muted}Jul 17,}\\ \small ID: nuD07vsk $\cdot$ \href{https://www.credly.com/go/nuD07vsk}{\color{accent}Verify}\\ \small\color{muted} Introduction to essential professional skills, communication, collaboration, adaptability, and career development.

\vspace{4pt}
\textbf{Getting Started with Artificial Intelligence} --- IBM SkillsBuild $\cdot$ \href{https://www.credly.com/badges/de0e7fd4-8593-48c7-95f6-104af1769c4e/linked\_in?t=t3kl17}{\color{accent}Verify}\\ \small\color{muted} Comprehensive introduction to Artificial Intelligence concepts, ethical AI, and practical applications across industries.

\vspace{4pt}
\textbf{Deep Learning using TensorFlow} --- IBM\\ \small\color{muted} Deep learning concepts including CNNs, RNNs, and autoencoders using TensorFlow.

\vspace{4pt}
\textbf{IBM Watson Services – Rapid Development} --- IBM\\ \small\color{muted} Job training in building chat widgets and AI services rapidly with IBM Watson.

\vspace{4pt}
\textbf{Introduction to Artificial Intelligence} --- Simplilearn SkillUp\\ \small\color{muted} Overview of AI techniques, applications, and basic algorithms.

\vspace{4pt}
\textbf{Introduction to Generative AI Studio} --- Google Cloud + Simplilearn\\ \small\color{muted} Practical generative AI studio skills using Google Cloud tools.

\vspace{4pt}
\textbf{Machine Learning} --- Ethnotech Academy\\ \small\color{muted} Practical ML training with regression, classification, and clustering implementation.

\vspace{4pt}
\textbf{Machine Learning} --- Intel EdGate Technologies\\ \small\color{muted} Industrial training utilizing Intel solutions and tools for ML.

\vspace{4pt}
\textbf{Predictive Analytics using IBM SPSS Modeler} --- IBM\\ \small\color{muted} Data mining and predictive analytics modeling using IBM SPSS.

\vspace{4pt}
\textbf{AWS Academy Cloud Foundations} --- AWS Academy $\cdot$ \href{https://www.credly.com/badges/850a46b9-cd01-46eb-a853-35550567b86c/linked\_in?t=t3kloq}{\color{accent}Verify}\\ \small\color{muted} Graduate training badge in AWS cloud fundamentals and architecture — covering core services, pricing, and security.

\vspace{4pt}
\textbf{Solution Architecture} --- AWS + Forage $\cdot$ \href{https://media.licdn.com/dms/image/v2/D4E22AQEGpdCmKHz7zA/feedshare-shrink\_800/B4EZddSqCDHYAg-/0/1749616862439?e=1766620800\&v=beta\&t=\_TCJKrqS71aJvjW24OvR1IKrAknmvRVPPPjzfHIsnjY}{\color{accent}Verify}\\ \small\color{muted} Job simulation in designing scalable, resilient solution architectures for enterprise-grade systems.

\vspace{4pt}
\textbf{Journey to Cloud} --- IBM SkillsBuild $\cdot$ \href{https://www.credly.com/badges/85e4145d-ecb3-4b8f-bb30-e4e47b4a26cc/linked\_in?t=t3kkzf}{\color{accent}Verify}\\ \small\color{muted} Envisioning cloud-first solutions, digital transformation strategies, and enterprise architecture design.

\vspace{4pt}
\textbf{Azure Fundamentals} --- Skillsoft $\cdot$ \href{https://skillsoft.digitalbadges.skillsoft.com/481daa56-525f-46d3-b249-ff884ef8ee85}{\color{accent}Verify}\\ \small\color{muted} Microsoft Azure cloud computing essentials — virtual machines, storage, networking, and identity management.

\vspace{4pt}
\textbf{Microsoft Azure Fundamentals} --- Infosys Springboard\\ \small\color{muted} Microsoft Azure cloud computing foundations and services overview.

\vspace{4pt}
\textbf{Web Development Fundamentals} --- IBM SkillsBuild $\cdot$ \href{https://www.credly.com/badges/2977f3c8-acb9-4ad3-a4fb-37ce1220d25d/linked\_in\_profile}{\color{accent}Verify}\\ \small\color{muted} Full-stack web development covering front-end technologies, responsive design, and modern deployment pipelines.

\vspace{4pt}
\textbf{Front-End Web Development Internship} --- IBM SkillsBuild \& Edunet Foundation\\ \small\color{muted} Front-End Web Development Internship certification.

\vspace{4pt}
\textbf{Website Development Tutorial} --- Infosys Springboard\\ \small\color{muted} Practical training in website layout and styling.

% ─── Achievements ────────────────────────────────────────────────────────────
\section{Achievements \& Badges}
\textbf{Prepare Data for ML APIs} --- Google Cloud \hfill \textit{\small\color{muted}Apr 14,}\\ \small\href{https://www.credly.com/badges/d6534857-e7f5-49d5-be4c-d40a91e5cb48}{\color{accent}View Badge}

\vspace{3pt}
\textbf{Deep Learning using TensorFlow} --- IBM \hfill \textit{\small\color{muted}Mar 30,}\\ \small\href{https://www.credly.com/badges/a289455e-4038-4810-a13d-f07613725b8b}{\color{accent}View Badge}

\vspace{3pt}
\textbf{IT Specialist – Artificial Intelligence} --- Certiport (Pearson VUE) \hfill \textit{\small\color{muted}Dec 16,}\\ \small\href{https://www.credly.com/badges/851d7a73-3caf-4851-baeb-52645964d1be}{\color{accent}View Badge}

\vspace{3pt}
\textbf{AWS Academy – Cloud Foundations} --- Amazon Web Services \hfill \textit{\small\color{muted}Jan 10,}\\ \small\href{https://www.credly.com/badges/850a46b9-cd01-46eb-a853-35550567b86c}{\color{accent}View Badge}

\vspace{3pt}
\textbf{Web Development Fundamentals} --- IBM SkillsBuild \hfill \textit{\small\color{muted}Oct 3, }\\ \small\href{https://www.credly.com/badges/2977f3c8-acb9-4ad3-a4fb-37ce1220d25d}{\color{accent}View Badge}

\vspace{3pt}
\textbf{Journey to Cloud: Envisioning Your Solution} --- IBM SkillsBuild \hfill \textit{\small\color{muted}Jul 16,}\\ \small\href{https://www.credly.com/badges/85e4145d-ecb3-4b8f-bb30-e4e47b4a26cc}{\color{accent}View Badge}

\vspace{3pt}
\textbf{Getting Started with AI} --- IBM SkillsBuild \hfill \textit{\small\color{muted}2025}\\ \small\href{https://www.credly.com/badges/de0e7fd4-8593-48c7-95f6-104af1769c4e}{\color{accent}View Badge}

\vspace{3pt}
\textbf{Project Management Fundamentals} --- IBM SkillsBuild \hfill \textit{\small\color{muted}Jul 17,}\\ \small\href{https://www.credly.com/go/cRerp16F}{\color{accent}View Badge}

\vspace{3pt}
\textbf{Lifelong Professional Skills} --- IBM SkillsBuild \hfill \textit{\small\color{muted}Jul 17,}\\ \small\href{https://www.credly.com/go/nuD07vsk}{\color{accent}View Badge}

% ─── Footer note ─────────────────────────────────────────────────────────────
\vspace{8pt}
\begin{center}
  \small\color{muted}
  Auto-generated on 20 July 2026 $\cdot$ Powered by Supabase + GitHub Actions
\end{center}

\end{document}
